Improving the Reliability of the Pavlovian Go/No-Go Task

### 2023-04-21 manuscript/main.tex
checkpointing manuscript progress (3)

A total of N=148 participants were recruited from Amazon Mechanical Turk (via CloudResearch; \cite{litman2017turkprime}) in May, 2020 to participate in an online behavioral experiment. Participants were eligible to participate if they were at least 18 years old and resided in the United States. Following best practice recommendations \cite{robinson2019tapped}, no other inclusion criteria were applied. This study was approved by the Institutional Review Board of Princeton University (\#5291), and all participants provided informed consent. Total study duration was 15-20 minutes. Participants received monetary compensation for their time (rate USD \$12/hr), plus an incentive-compatible bonus up to \$1.50 based on task performance.

@@

%TC:ignore
\begin{figure}[t]
    \centerline{\includesvg[inkscapelatex=false,width=1.00\textwidth]{figures/fig01.svg}}
    \caption{}
    \label{fig:task_schematic}
\end{figure}
%TC:endignore

@@

We fit a set of seven nested reinforcement learning (RL) models to participants' choice data. All models are variants of the Rescorla-Wagner model and have previously been used to predict choice behavior on this task \cite{guitart2012go, mkrtchian2017modeling}. In the base model (M1), the probability of choosing an action is determined by the difference in stimulus-action values, scaled an outcome sensitivity parameter ($\beta$), and passed through the logistic function. In turn, action values are learned via the Rescorla-Wagner update rule as governed by a learning rate ($\eta$). The next model (M2) is augmented with a static approach/avoidance parameter ($\tau$) that biases action towards go and no-go responses when $\tau > 0$ and $\tau < 0$, respectively. The next model (M3) has independent approach/avoidance parameters per outcome domain ($\tau_+$, $\tau_-$). The succeeding models have either independent outcome sensitivity  ($\beta_+$, $\beta_-$; M4) or learning rate parameters ($\eta_+$, $\eta_-$; M5) per outcome domain. The penultimate model (M6) separates all three parameter types by outcome domain. Finally, the most complex model (M7) adds a lapse rate ($\xi$). Full equations and model descriptions are provided in the Supplementary Materials.

All models were estimated within a hierarchical Bayesian modeling framework using Hamiltonian Monte Carlo as implemented in Stan (v2.30; \cite{carpenter2017stan}). For each model, four separate chains with randomized start values each took 7,500 samples from the posterior. The first 5,000 samples, and every-other subsequent sample, from each chain were discarded. Thus, 5,000 post-warmup samples from the joint posterior were retained. The $\hat{R}$ values for all parameters were $\leq 1.01$, indicating acceptable convergence between chains, and there were no divergent transitions in any chain. Our choices of prior are detailed in the Supplementary Materials. Briefly, we specified diffuse and uninformative priors to avoid biasing parameter estimation.

@@

%TC:ignore
\begin{figure}[b!]
    \centerline{\includesvg[inkscapelatex=false,width=1.00\textwidth]{figures/fig05.svg}}
    \caption{Summary of reinforcement learning model parameters. (A) Group-level model parameters for each session. Error bars indicate 95\% HDIs. **Denotes pairwise comparison where 95\% HDI of the difference excludes zero. (B) Test-retest reliability estimates for each model parameter. Filled circles denote estimates for Experiment 2; open circles denote estimates from Experiment 1. The grey vertical lines show the change in reliability across experiments. Dotted lines indicates average reliability for Experiment 2. Shaded region indicates conventional range of acceptable reliability ($\rho \geq 0.7$).}
    \label{fig:exp02_modeling}
\end{figure}
%TC:endignore

@@

Our results constitute a marked improvement in parameter reliability over previous studies. Moutoussis and colleagues \cite{moutoussis2018change} first reported poor reliability of models parameters for hte Pavlovian go/no-go task. However, they studied performance in a developmental sample (14 - 24 yrs) over long retest intervals (6 mo, 18 mo), begging the question whether poor reliability reflected actual changes in the sample (with age), retest interval, or both. Recently, Pike and colleagues \cite{pike2022test} investigated reliability in an online sample of adults using a two-week retest interval and similarly found poor reliability, suggesting the issue is not specific. Our improved reliability likely reflect a confluence of factors. First, our task utilized gamification principles, which may have improved reliability by maximizing participant engagement and/or minimizing participant confusion. Gamification has previously been found to improve the reliability of cognitive tasks \cite{kucina2022solution, verdejo2021unified}. A second possibility is that previous studies suffered from practice effects, which can hamper reliability by minimizing between-participants variability and if changes are not uniform (e.g., interactions with age; \cite{anokhin2022age}). Indeed, by minimizing practice effects, we saw large improvements in reliability. A third possibility is use of method. Hierarchical Bayesian methods have been to minimize estimation noise and thereby improve reliability estimates \cite{brown2020improving, waltmann2022sufficient}.

We also found large practice effects in the original version of the task. We note that practice effects are common to cognitive tasks \cite{hausknecht2007retesting, scharfen2018retest}. More specifically, Moutoussis found evidence of practice even despite their long retest intervals \cite{moutoussis2018change}. Our solution was to redesign the task to prevent alternative strategies. By preventing participants from becoming aware of critical elements of the task design, one can improve the stability of behavior over time (and also improve reliability) \cite{mclean2018towards}.

% The current study is not without limitations. We have investigated the reliability of our modified Pavlovian go/no-go task only in a sample of online adult participants. Reliability is not constant, however, but can vary as a function of sample and setting. For example, our task may be adequately reliable for healthy adult participants, but that may not be the case for developmental or patient populations. Previous evidence suggests the task requires working memory, and our version of the task is more difficult, thus may be challenging. New studies are required.

The current study is not without limitations. Here we have investigated the psychometric properties of our modified Pavlovian go/no-go task only in a sample of online adult participants. The reliability of a task measure, however, is not absolute; reliability can vary as a function of participant demographics and the context in which the task is administered. For example, previous investigations have found that the reliability of task measures in healthy adults is not the same for psychiatric and developmental samples \cite{cooper2017role, arnon2020current}. To the extent that Pavlovian-instrumental interactions are modulated by executive functioning (i.e., working memory; \cite{swart2017catecholaminergic, chen2023effect}), it may be that the new version of this task proves too challenging for other subpopulations and diminish reliability. Additional studies are necessary to validate this modified version of the task in other populations.

A second limitation is that we only studied choice, not response times. Pavlovian biases extend into response times, and these two might be a reliable source of individual differences. Discuss one or two dstudies. Joint modeling may further improve reliability by virtue of improving parameter estimation. For example, the joint modeling of choice and response time has been found to improve the precision and reliability of estimated parameters in reinforcement learning \cite{ballard2019joint, shahar2019improving}.

% is Hanneke's RT study out?

% conclusion: tolerability.

@@

In Experiment 2, prior to starting the task, participants completed the same set of self-report questionnaires except that the 7-up/7-down was replaced with the 7-item depression subscale from the depression, anxiety, and stress scale (DASS; \cite{henry2005short}). Participants completed the BIS/BAS scale once, on Day 0 only. Participants completed the GAD-7, DASS, and mood slider scales at the start of every session.

@@

@@

To better characterize participants' performance on the Pavlovian go/no-go task, we fit a nested set of reinforcement learning models to their choice data. Models were adapted from previous studies of this task. We start with the most complex model, in which all simpler models are nested. Under this model, the probability that a participant makes a Go response in response to stimulus $k$ is defined as:
\begin{equation}
    p(y_{k} = 1) = 0.5 \cdot \xi + (1 - \xi) \cdot \text{logit}^{-1} \left( \beta_{v_k} \cdot [Q_k(\text{Go}) - Q_k(\text{NoGo})] + \tau_{v_k} \right)
\end{equation}
where $Q_k(\text{Go})$ and $Q_k(\text{NoGo})$ are the current learned values of a Go and No-Go response, respectively; $\beta_{v_k}$  is the inverse temperature (choice sensitivity) parameter for stimuli of a particular valence (gain, loss); $\tau_{v_k}$ is the go bias for stimuli of a particular valence; and $\xi$ is the lapse rate. In turn, the value of a choice option is learned through feedback and a learning rule:
\begin{equation}
    Q_k(\text{action}) \leftarrow \eta_{v_k} \cdot \left[ r - Q_k(\text{action}) \right]
\end{equation}
where $r$ is the observed outcome on a particular trial; and $\eta_{v_k}$ is the learning rate for stimuli of a particular valence. For all models, outcomes were rescaled so that the better and worse of the two possible outcomes were equal to one and zero, respectively. Moreover, the Q-values are initialized at 0.5. Simplified versions of this model involved either fixing parameters to be equal regardless of the outcome domain (e.g., $\beta_{+} = \beta_-$) and/or fixing other parameters to zero (e.g., $\xi = 0$).

@@

\begin{figure}[h]
    \centerline{\includesvg[inkscapelatex=false,width=1.00\textwidth]{figures/figS01.svg}}
    \caption{Caption}
    \label{fig:figS01}
\end{figure}

@@

\begin{figure}[h]
    \centerline{\includesvg[inkscapelatex=false,width=1.00\textwidth]{figures/figS04.svg}}
    \caption{Caption}
    \label{fig:figS04}
\end{figure}

@@

\begin{figure}[h]
    \centerline{\includesvg[inkscapelatex=false,width=1.00\textwidth]{figures/figS05.svg}}
    \caption{Caption}
    \label{fig:figS05}
\end{figure}

@@

>>>>

A total of N=148 participants were recruited from Amazon Mechanical Turk (via CloudResearch; \cite{litman2017turkprime}) in May, 2020 to participate in an online behavioral experiment. Participants were eligible to participate if they were at least 18 years old and resided in the United States. Following best practice recommendations \cite{robinson2019tapped}, no other inclusion criteria were applied. This study was approved by the Institutional Review Board of Princeton University (\#5291), and all participants provided informed consent. Total study duration was 15-20 minutes. Participants received monetary compensation for their time (rate: USD \$12/hr), plus an incentive-compatible bonus up to \$1.50 based on task performance.

@@

%TC:ignore
\begin{figure}[t]
    \centerline{\includesvg[inkscapelatex=false,width=1.00\textwidth]{figures/fig01.svg}}
    \caption{(A) Schematic of the Pavlovian go/no-go task. On each trial, a robot entered the `scanner' from the left of screen, prompting a response (go or no-go) from the participant during a response window (Experiment 1: 1.5 seconds; Experiment 2: 1.3 seconds). The outcome (number of points won or lost) was subsequently presented (Experiment 1: 1.0 seconds; Experiment 2: 1.2 seconds), followed by an inter-trial interval animation (1 second) in which the conveyer belt carried the old robot out of view and a new robot into the scanner. The color of the scanner light denotes outcome domain (e.g., blue denotes reward and red denotes punishment). (B) The four trial types, produced by a factorial combination of outcome domain (rewarding, punishing) and correct action (go, no-go). C) Outcome probabilities for each outcome domain following a correct or incorrect response. Correct responses yielded the better of the two possible outcomes with 80\% chance. (D) Trial composition. In Experiment 1, participants saw 8 total robots (two of each trial type), each presented for 30 trials (240 total trials). In Experiment 2, participants saw 24 total robots (6 of each trial type), each between for 8, 10, or 12 trials (240 total trials).}
    \label{fig:task_schematic}
\end{figure}
%TC:endignore

@@

We fit a set of seven nested reinforcement learning (RL) models to participants' choice data. All models are variants of the Rescorla-Wagner model and have previously been used to predict choice behavior on this task \cite{guitart2012go, mkrtchian2017modeling, moutoussis2018change, swart2017catecholaminergic}. In the base model (M1), the probability of choosing an action is determined by the difference in stimulus-action values, scaled an outcome sensitivity parameter ($\beta$), and passed through the logistic function. In turn, action values are learned via the Rescorla-Wagner update rule as governed by a learning rate ($\eta$). The next model (M2) is augmented with a static approach/avoidance parameter ($\tau$) that biases action towards go and no-go responses when $\tau > 0$ and $\tau < 0$, respectively. The next model (M3) has independent approach/avoidance parameters per outcome domain ($\tau_+$, $\tau_-$). The succeeding models have either independent outcome sensitivity  ($\beta_+$, $\beta_-$; M4) or learning rate parameters ($\eta_+$, $\eta_-$; M5) per outcome domain. The penultimate model (M6) separates all three parameter types by outcome domain. Finally, the most complex model (M7) adds a lapse rate ($\xi$). Full equations and model descriptions are provided in the Supplementary Materials.

All models were estimated within a hierarchical Bayesian modeling framework using Hamiltonian Monte Carlo as implemented in Stan (v2.30; \cite{carpenter2017stan}). See the Supplementary Materials for details about model estimation and our choices of prior. Briefly, we specified diffuse and uninformative priors to avoid biasing parameter estimation.

@@

%TC:ignore
\begin{figure}[t!]
    \centerline{\includesvg[inkscapelatex=false,width=1.00\textwidth]{figures/fig05.svg}}
    \caption{Summary of reinforcement learning model parameters. (A) Group-level model parameters for each session. Error bars indicate 95\% HDIs. **Denotes pairwise comparison where 95\% HDI of the difference excludes zero. (B) Test-retest reliability estimates for each model parameter. Filled circles denote estimates for Experiment 2; open circles denote estimates from Experiment 1. The grey vertical lines show the change in reliability across experiments. Dotted lines indicates average reliability for Experiment 2. Shaded region indicates conventional range of acceptable reliability ($\rho \geq 0.7$).}
    \label{fig:exp02_modeling}
\end{figure}
%TC:endignore

@@

% Given the prominent role of threat conditioning paradigms in preclinical and clinical-translational research, it is important to assess the reliability of these protocols over time in the same individuals. Here, we investigated the test–retest reliability of two behavioral measures during auditory threat acquisition and stimulus generalization tests, SCR and risk ratings, across a 1-to-2-week interval. Our primary goal was to assess the test–retest of threat generalization. For SCR, reliability was generally fair across two types of G coefficients, one indexing within-person stability of response patterns and the other indexing reliability of change across time. However, reliability was notably poorer for risk ratings. Additionally, generalization gradients did not significantly differ at each time-point, although there was some across session variability at the level of individual stimuli. These results provide moderate support for the conclusion that threat generalization gradients remain relatively stable using an identical protocol at two timepoints, but in line with prior work, that reliability is modest in magnitude and related to the specific type of measure. These findings provide useful information regarding the utility of these paradigms for pre-to-post measures on the efficacy of behavioral interventions aimed at reducing generalized fear and arousal (e.g., cognitive behavioral therapy or cognitive bias modification for anxiety disorders; Cristea et al., 2015; Steinman et al., 2021).

The test-retest reliability of reinforcement learning model parameters observed here are markedly improved compared to previous studies \cite{moutoussis2018change, pike2022test}. Indeed, previous studies investigating the reliability of both descriptive and model-based behavioral measures of performance on the Pavlovian go/no-task found them to be moderate-to-poor in range. The discrepancy in findings between ours and past studies likely reflect a confluence of factors. First, our task made use of gamificiation principles intended to promote participant engagement and minimize confusion, which has previously been found to improve the reliability of cognitive task measures \cite{kucina2022solution, verdejo2021unified}. A second possibility is that, similar to our Experiment 1, previous studies were hampered by practice effects. Practice effects can substantially impact reliability when they are not uniformly expressed by participants, such as when they manifest as a function of age \cite{anokhin2022age}. Indeed we observed the largest improvements in parameter reliability after minimizing practice effects in Experiment 2. A third possibility is our use of method. By exploiting partial-pooling, hierarchical Bayesian models have been shown to minimize parameter estimation noise and thereby improve reliability estimates \cite{haines2023classical, rouder2019psychometrics}. Previous empirical studies have demonstrated the impact of hierarchical Bayesian models for improving reliability estimates \cite{brown2020improving, waltmann2022sufficient}.

Relatedly, we also observed large practice effects for the standard version of the task (Experiment 1). This is not in itself surprising, as practice effects are common to cognitive tasks in general \cite{hausknecht2007retesting, scharfen2018retest} and were previously observed for the Pavlovian go/no-go task (even across lengthy retest intervals; \cite{moutoussis2018change}). In our case, participants appeared to be using a qualitatively different behavioral strategy to complete the task after the initial administration. Specifically, participants ostensibly exploited acquired knowledge of the task structure to utilize a ``process-of-elimination'' strategy that allowed them to identify the correct response to certain quickly and without the need for trial-and-error (i.e., reinforcement) learning. Our solution was to redesign the task in such a way to prevent such strategies from forming or being advantageous to use. This approach is similar to previous studies, where preventing participants from becoming aware of critical elements of the task design improved both the consistency and reliability of behavior even with practice \cite{mclean2018towards}.

The current study is not without limitations. Here we have only investigated the psychometric properties of our modified Pavlovian go/no-go task in a sample of online adult participants. The reliability of task measures, however, are not absolute; reliability can vary by participant demographics and the experiment setting. For example, previous studies have found that the reliability of specific task measures in healthy adults is not the same as for adults with psychopathology \cite{cooper2017role} or healthy children \cite{arnon2020current}. To the extent that our modified version of the Pavlovian go/no-go task is more challenging (see \ref{tab:tabS02}), it may be the case that it proves too challenging for other groups, which may harm reliability (e.g., \cite{arnon2020current}). Additional studies are necessary to validate this version of the task in other populations. It should also be noted that the current study is not necessarily informative about the reliability of Pavlovian biases over longer periods of time (i.e., beyond 2--4 weeks).

A second limitation is that we studied only choice but not response times. Previous studies have found that Pavlovian biases manifest in response times in addition to choice behavior \cite{millner2018pavlovian, algermissen2022striatal}, and may be a meaningful index of individual-differences in behavior \cite{betts2020learning, millner2019suicidal, scholz2020dissociable}. Furthermore, previous studies have introduced computational frameworks for jointly modeling participants' choice and response time behavior on the task \cite{millner2018pavlovian, millner2019suicidal}. This is notable because the joint modeling of choice and response time has previously been found to improve the precision and reliability of estimated parameters in reinforcement learning models \cite{ballard2019joint, shahar2019improving}. Therefore, future research should investigate how the reliability of model-based measures of behavior on the Pavlovian go/no-go task could be further improved by incorporating response times.

Limitations notwithstanding, our study demonstrates that it is possible to derive behavioral measures from the Pavlovian go/no-go task that are sufficiently reliable for use in individual-differences research. We encourage researchers to use and further adapt the modified version of the task presented here. In support of this, we have made all of our data and code publicly available (see Code Availability).

@@

In Experiment 2, prior to starting the task, participants completed the same set of self-report questionnaires with the exception that the 7-up/7-down was replaced with the 7-item depression subscale from the depression, anxiety, and stress scale (DASS; \cite{henry2005short}). Participants completed the BIS/BAS scale once, on Day 0 only. Participants completed the GAD-7, DASS, and mood slider scales at the start of every session.

@@

To ensure data quality in Experiments 1 and 2, the data from multiple participants from the initial session were excluded prior to analysis. In Experiment 1, the data from multiple participants who completed the experiment on Day 0 were excluded prior to analysis for one or both of the following reasons: failing more than one attention check embedded in the self-report measures (N=13) or exhibiting chance-level performance ($<$55\% correct responses) on go to win trials (N=43). Data from N=45 participants who completed the first session were excluded under these criteria, leaving a final sample of N=103 participants. No exclusions were applied to subsequent session data.

In Experiment 2, the data from multiple participants who completed the experiment on Day 0 were excluded prior to analysis for one or both of the following reasons: failing one or more attention checks embedded in the self-report measures (N=30); making go or no-go responses on more than 90\% of trials (N=5); exhibiting chance-level performance ($<$55\% correct responses) across all trials (N=22). Data from N=46 participants who completed the first session were excluded under these criteria, leaving a final sample of N=110 participants. No exclusions were applied to subsequent session data.

@@

To more precisely characterize participants' performance on the Pavlovian go/no-go task in Experiments 1 and 2, we fit a nested set of reinforcement learning models to their choice data.  All models are variants of the Rescorla-Wagner model and have previously been used to predict choice behavior on this task \cite{guitart2012go, mkrtchian2017modeling, moutoussis2018change, swart2017catecholaminergic}. Under the most complex model (M7), the probability that a participant makes a go response following stimulus $k$ is defined as:
\begin{equation}
    p(y = \text{go}) = (1 - \xi) \cdot \text{logit}^{-1} \left( \beta_{v_k} \cdot [Q_k(\text{Go}) - Q_k(\text{NoGo})] + \tau_{v_k} \right) + \frac{\xi}{2}
\end{equation}
where $Q_k(\text{go})$ and $Q_k(\text{no-go})$ are the learned stimulus-action values for the go and no-go responses, respectively; $\beta_{v_k}$ is the reward sensitivity (if stimulus $k$ is rewarding) or punishment sensitivity (if stimulus $k$ is punishing) parameter; $\tau_{v_k}$ is an approach bias (if stimulus $k$ is rewarding) or avoidance bias (if stimulus $k$ is punishing) parameter; and $\xi$ is the lapse rate. In turn, the value of a response is learned through feedback according to a learning rule:
\begin{equation}
    Q_k(\text{action}) \leftarrow \eta_{v_k} \cdot \left[ r - Q_k(\text{action}) \right]
\end{equation}
where $r$ is the observed outcome on a particular trial; and $\eta_{v_k}$ is the positive learning rate (if stimulus $k$ is rewarding) or the negative learning rate (if stimulus $k$ is punishing). In all models, outcomes were rescaled so that the the better and worse of the two possible outcomes were equal to one and zero, respectively. The Q-values were accordingly initialized to $Q = 0.5$.

Simplifications of this model involved either fixing parameters to be equal to zero or fixing parameters to be equal their counterpart. Specifically, the base model (M1) had two free parameters: a single outcome sensitivity parameter and a single learning rate, both shared across outcome domains (i.e., $\beta_+ = \beta_-$; $\eta_+ = \eta_-$; $\tau_+ = \tau_- = 0$). Model 2 added a static bias parameter that was shared across outcome domains (i.e., $\tau_+ = \tau_-$). Model 3 relaxed this assumption and involved for independent approach ($\tau_+$) and avoidance ($\tau_-$) parameters. The next two models involved independent outcome sensitivity ($\beta_+, \beta_-$; M4) or learning rate ($\eta_+, \eta_-$; M5) parameters by outcome domain. Model 6 involved both independent outcome sensitivity and learning rate parameters. Finally, the most complex model (M7) included a lapse rate ($\xi$).

All models were estimated within a hierarchical Bayesian modeling framework using Hamiltonian Monte Carlo as implemented in Stan (v2.30; \cite{carpenter2017stan}). For each model, four separate chains with randomized start values each took 7,500 samples from the posterior. The first 5,000 samples, and every-other subsequent sample, from each chain were discarded. Thus, 5,000 post-warmup samples from the joint posterior were retained. The $\hat{R}$ values for all parameters were $\leq 1.01$, indicating acceptable convergence between chains, and there were no divergent transitions in any chain. For all models, we specified diffuse, uninformative priors in order to avoid biasing parameter estimation (Table \ref{tab:priors}).

@@

\begin{figure}[h]
    \centerline{\includesvg[inkscapelatex=false,width=1.00\textwidth]{figures/figS01.svg}}
    \caption{The trial structure of an example block of the modified Pavlovian go/no-go task. In one task block, there are 12 unique stimuli (three of each trial type: go to win [GW; dark blue]; no-go to win [NGW; light blue]; go to avoid losing [GAL; light red]; no-go to avoid losing [NGAL; dark red]) divided into three sets (Set 1: empty circles; Set 2: half-filled circles; Set 3: filled circles). Each set is composed of approximately 40 trials (120 trials total). Each set, however, may not involve all four trial types. In the example block above, Set 1 involves two NGAL stimuli and zero GAL stimuli; in turn, Set 2 involves two GAL stimuli and zero NGAL stimuli.}
    \label{fig:figS01}
\end{figure}

@@

\begin{figure}[h]
    \centerline{\includesvg[inkscapelatex=false,width=1.00\textwidth]{figures/figS04.svg}}
    \caption{Split-half reliability estimates for the best-fitting model parameters for Experiment 1 (A) and Experiment 2 (B). Filled circles denote estimates for each experiment; open circles denote estimates from Experiment 1. The grey vertical lines show the change in reliability across experiments. Dotted lines indicates average reliability. Shaded region indicates conventional range of acceptable reliability ($\rho \geq 0.7$).}
    \label{fig:figS04}
\end{figure}

@@

\begin{figure}[h]
    \centerline{\includesvg[inkscapelatex=false,width=1.00\textwidth]{figures/figS05.svg}}
    \caption{Summary of self-report measures indicating that mood and anxiety across participants were relatively stable over the study period. (A) Group-level mood and symptom scores for each session. Error bars indicate 95\% HDIs. **Denotes significant pairwise comparison. (B) Test-retest reliability estimates for each model parameter. Dotted lines indicates overall average. Shaded region indicates conventional range of acceptable reliability ($\rho \geq 0.7$).}
    \label{fig:figS05}
\end{figure}

@@

\clearpage
\subsection*{Priors for hierarchical Bayesian reinforcement learning models}

\begin{table}[h!]
    \centering
    \begin{tabular}{llll}
        \toprule
                  &                   & \multicolumn{2}{c}{Group-level} \\
        \cmidrule(lr){3-4}
        Parameter & \multicolumn{1}{c}{Participant-level} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Std. Dev.} \\
        \midrule
        Outcome sensitivity & $\beta_i \sim 10 \cdot \mathcal{N}(\mu_\beta, \sigma_\beta)$ & $\mu_\beta \sim \mathcal{N}(0,1)$ & $\sigma_\beta \sim \text{Student-}t(3,0,1)$ \\ 
        Approach/avoidance bias & $\tau_i \sim 5 \cdot \mathcal{N}(\mu_\tau, \sigma_\tau)$ & $\mu_\tau \sim \mathcal{N}(0,1)$ & $\sigma_\tau \sim \text{Student-}t(3,0,1)$ \\ 
        Learning rate & $\eta_i \sim \Phi \left(\mathcal{N}(\mu_\eta, \sigma_\eta)\right)$ & $\mu_\eta \sim \mathcal{N}(0,1)$ & $\sigma_\eta \sim \text{Student-}t(3,0,1)$ \\ 
        Lapse rate & $\xi_i \sim \Phi \left(-2 + \mathcal{N}(\mu_\xi, \sigma_\xi)\right)$ & $\mu_\xi \sim \mathcal{N}(0,1)$ & $\sigma_\xi \sim \text{Student-}t(3,0,1)$ \\ 
        \bottomrule
    \end{tabular}
    \caption{Participant- and group-level priors specified for each parameter in the hierarchical Bayesian reinforcement learning models. Notes: $\Phi$ denotes the cumulative density function for the standard normal distribution (used to constrain learning and lapse rates to be in the range $[0,1]$).}
    \label{tab:priors}
\end{table}
